---
title: "diversity"
author: "Shiyu Yang"
date: "2024-11-03"
output: html_document
---
This RMD file is build to explore Shiyu's second research question: Whether women and BIPOC authors collaborate with in-group members and other underrepresented members?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(emmeans)
library(gamlss)
```

# Read data

## Publication-level data

```{r}
publication_data<- read.csv("updating_full_data.csv") 
```

## Author-level data

```{r}
raw_author_data<- read.csv("updating_gender_bipoc_data.csv") 

# Correct class to factor and remove duplicate authors
author_data<- raw_author_data%>% 
  mutate(bipoc = as.factor(bipoc),
         gender = as.factor(gender)) %>% 
  distinct()
```

# Data Wrangling

## Exclude first author in all publications

```{r}
# Exclude first author
author_exclude<- author_data %>% 
  group_by(doi) %>%
  mutate(author_rank = row_number()) %>% 
  filter(author_rank > 1) %>%          
  ungroup() %>%                        
  select(-author_rank)

# Don't exclude any author
author<- author_data %>% 
  group_by(doi) %>%
  mutate(author_rank = row_number()) %>% 
  filter(author_rank > 1) %>%          
  ungroup() %>%                        
  select(-author_rank)

# Calculate the actual count in all publications
author_prop <- author %>%
  group_by(publication_year, gender, bipoc) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(publication_year) %>%
  mutate(proportion = count / sum(count))

# Calculate women proportion in overall
overall_women_proportion <- sum(author_prop$count[author_prop$gender == 1], na.rm = TRUE) /
  sum(author_prop$count, na.rm = TRUE)
#37%

# Calculate BIPOC proportion in overall
overall_bipoc_proportion <- sum(author_prop$count[author_prop$bipoc == 1], na.rm = TRUE) /
  sum(author_prop$count, na.rm = TRUE)
#25%
```

The overall_women_proportion represents among all publication from 2009-2024.

## First author & collaboation

```{r}
# Calculate the women and BIPOC proportion after excluding first author
first_data <- author_exclude %>%
  dplyr::select(author_full_names, doi, gender, bipoc) %>% 
  group_by(doi) %>%
  summarize(
    author_counts = n() ,  
    women_prop = mean(gender == "1", na.rm = TRUE),  
    bipoc_prop = mean(bipoc == "1", na.rm = TRUE)
  )

# Filter data
data <- publication_data %>%
  dplyr::filter (overlap_corr_author == "1"|overlap_corr_author == "2") %>% 
  dplyr::select(doi, cited_count,first_author_gender, first_author_bipoc, publication_year, journal, author_count, document_type, fund, affiliation_us,single_author) %>%
  left_join(first_data, by = "doi") %>% 
  dplyr::filter (single_author == "0") %>% 
  mutate(publication_year = 2024 - publication_year) %>% 
  mutate(across(c(single_author,fund,affiliation_us,
                  first_author_bipoc, first_author_gender, document_type, journal), 
                as.factor)) %>% 
  filter(!is.na(first_author_gender), !is.na(first_author_bipoc),
         !is.na(women_prop), !is.na(bipoc_prop),!is.na(author_counts))
  

#colSums(is.na(data)) # Check NAs

# Center data for data analysis
data$publication_year_c <- data$publication_year - mean(data$publication_year, na.rm = T)
data$author_count_c <- data$author_count - mean(data$author_count, na.rm = T)
```

## Last author & collaboration

```{r}
# Calculate the women and BIPOC proportion after excluding last author
last_author_data  <- author_data %>%
  dplyr::select(author_full_names, doi, gender, bipoc) %>%
  group_by(doi) %>%
  slice(1:(n() - 1)) %>%  
  summarize(
    author_counts = n(),
    women_prop = mean(gender == "1", na.rm = TRUE),
    bipoc_prop = mean(bipoc == "1", na.rm = TRUE)
  )

# Filter data
data_last <- publication_data %>%
  dplyr::filter (overlap_corr_author == "1"|overlap_corr_author == "2") %>% 
  dplyr::select(doi, cited_count,last_author_gender, last_author_bipoc, publication_year, journal, author_count, document_type, fund, affiliation_us,single_author) %>%
  left_join(last_author_data, by = "doi") %>% 
  dplyr::filter (single_author == "0") %>% 
  mutate(publication_year = 2024 - publication_year) %>% 
  mutate(across(where(is.character), factor)) %>% 
  mutate(across(c(single_author,fund,affiliation_us,
                  last_author_bipoc, last_author_gender, document_type, journal), 
                as.factor)) %>% 
  filter(!is.na(last_author_gender), !is.na(last_author_bipoc),
         !is.na(women_prop), !is.na(bipoc_prop),!is.na(author_counts))

#colSums(is.na(data_last)) # Check NAs

# Center data for data analysis
data_last$publication_year_c <- data_last$publication_year - mean(data_last$publication_year, na.rm = T)
data_last$author_count_c <- data_last$author_count - mean(data_last$author_count, na.rm = T)
```

# EDA

## Author gender and BIPOC distribution in overall

```{r}
ggplot(data, aes(x = women_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#7F8993", color = "black") +
  labs(x = "Proportion of Women Authors", y = "Number of Publications") 

ggplot(data, aes(x = bipoc_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#dbc6d9", color = "black") +
  labs(x = "Proportion of BIPOC Authors", y = "Number of Publications") 

ggplot(data_last, aes(x = women_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#7F8993", color = "black") +
  labs(x = "Proportion of Women Authors", y = "Number of Publications") 

ggplot(data_last, aes(x = bipoc_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#dbc6d9", color = "black") +
  labs(x = "Proportion of BIPOC Authors", y = "Number of Publications") 
```

Heavy on tails (0 and 1), so I choose GAM with Beta-inflated distribution or GLM with quasibinomial distribution for data analysis. 

# Model fitting

```{r}
# GAM with Beta-inflated distribution

## Effect of first author gender and race on Women Proportion in each Publication, controlling effect of character of publications
m1_1 <- gamlss(women_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

## Effect of first author gender and race on BIPOC Proportion in each Publication, controlling effect of character of publications
m2_1 <- gamlss(bipoc_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

## Effect of last author gender and race on Women Proportion in each Publication, controlling effect of character of publications
m3_1 <- gamlss(women_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

## Effect of last author gender and race on BIPOC Proportion in each Publication, controlling effect of character of publications
m4_1 <- gamlss(bipoc_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

# GLM with quasibinomial distribution

## Effect of first author gender and race on Women Proportion in each Publication, controlling effect of character of publications
m1_2 <- glm(women_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data)

## Effect of first author gender and race on BIPOC Proportion in each Publication, controlling effect of character of publications
m2_2 <- glm(bipoc_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data)

## Effect of last author gender and race on Women Proportion in each Publication, controlling effect of character of publications
m3_2 <- glm(women_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data_last)

## Effect of last author gender and race on BIPOC Proportion in each Publication, controlling effect of character of publications
m4_2 <- glm(bipoc_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data_last)
```

## Model comparison

### Plots
```{r}
plot(m1_1) 
plot(m1_2) 
# m1_1 looks better
```

### RMSE with cross-validation

```{r}
# Set values
set.seed(123) 
k_folds <- 5
folds <- cut(seq(1, nrow(data)), breaks = k_folds, labels = FALSE)

rmse_gamlss <- numeric(k_folds)
rmse_glm <- numeric(k_folds)

# Loop for CV
for (i in 1:k_folds) {
  test_indices <- which(folds == i, arr.ind = TRUE)
  train_data <- data[-test_indices, ]
  test_data <- data[test_indices, ]
  m1 <- gamlss(
    women_prop ~ first_author_gender * first_author_bipoc +
      publication_year_c + fund + author_count_c +
      document_type + affiliation_us + journal,
    family = BEINF,
    data = train_data
  )
  predictions_gamlss <- predict(m1, newdata = test_data, type = "response")
  rmse_gamlss[i] <- sqrt(mean((test_data$women_prop - predictions_gamlss)^2))
  
  m2 <- glm(
    women_prop ~ first_author_gender * first_author_bipoc +
      publication_year_c + fund + author_count_c +
      document_type + affiliation_us + journal,
    family = quasibinomial(link = "logit"),
    data = train_data
  )
  predictions_glm <- predict(m2, newdata = test_data, type = "response")
  rmse_glm[i] <- sqrt(mean((test_data$women_prop - predictions_glm)^2))
}

avg_rmse_gamlss <- mean(rmse_gamlss)
# 0.26
avg_rmse_glm <- mean(rmse_glm)
# 0.25
```
Although the GLM has lower RMSE, compare to the plot, I will use GAM in the following analysis.

### Summary for model 1

```{r}
summary(m1_1)
```
 
After transformation, intercept is the baseline proportion of women proportion is approximately 38.5% when all predictors are at their reference levels.

The coefficient on first author gender indicates the publications with a woman first author have an 11.7% higher proportion of women authors compared to publication with a man first author.

The coefficient on first author BIPOC indicates the publications with a BIPOC first author have a 5.2% lower proportion of women authors compared to White first authors. 

The coefficient on centered publication year suggests for each additional year, the proportion of women authors in each publication increases by 1.1%.

The coefficient on US affiliation suggests publications from U.S.-based affiliations do not show a significant difference in the proportion of women authors.

The coefficient on fund suggests whether an publication is funded or not does not significantly affect the proportion of women authors

The coefficient on author count suggests the number of authors does not have a significant impact on the proportion of women authors.

The coefficient on document type suggests Review show no significant difference in the proportion of women authors compared to Article.

Publications in JoCN have a 5.7% higher BIPOC proportion compared to Brain, and publications in Nature Neuroscience have a 0.97% higher BIPOC proportion compared to Brain. The first one was significant but the latter one was not.

The coefficient on interaction term indicate there is no significant difference.


#### Visualization for model 1

```{r}
# Bar plot for first author gender and race effect on women proportion
m1_graph <- gamlss(women_prop ~ first_author_gender * first_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

fitted_values <- fitted(m1_graph)

results <- data.frame(
  first_author_gender = data$first_author_gender,
  first_author_bipoc = data$first_author_bipoc,
  affiliation_us = data$affiliation_us,
  fund = data$fund,
  document_type = data$document_type,
  journal = data$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(first_author_gender, first_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p1<- ggplot(predictions_summary, aes(x = factor(first_author_gender, levels = c(0, 1), 
                                    labels = c("Man", "Woman")), 
                     y = mean_pred, 
                     fill = factor(first_author_bipoc, levels = c(0, 1), 
                                   labels = c("White", "BIPOC"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "First Author Gender",
    y = "Predicted Women Proportion",
    fill = "First Author Race",
    title = "Predicted Women Proportion Based on First Author Gender and Race"
  ) +
  scale_fill_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 14),
    legend.position = "top"
  )
p1

ggsave("gender_collab_bar.png", plot = p1, width = 10, height = 6)
```

```{r}
# Line plot for first author gender and race effect over years on women proportion
predictions_summary_year <- results %>%
  group_by(first_author_gender, first_author_bipoc, publication_year = data$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p1_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 linetype = factor(first_author_bipoc, levels = c(0, 1), 
                                   labels = c("White", "BIPOC")),
                 color = factor(first_author_gender, levels = c(1, 0), 
                                labels = c("Woman", "Man")))) +
  geom_line(size = 1.5) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(first_author_gender, levels = c(1, 0), 
                                labels = c("Woman", "Man"))), 
              alpha = 0.07, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted Women Proportion",
    color = "First Author Gender",
    fill = "First Author Gender",
    linetype = "First Author Race",
    title = "Predicted Women Proportion Over Years"
  ) +
  scale_color_manual(values = c("Woman" = "#ccd4dd", "Man" = "#5e6777")) +
  scale_fill_manual(values = c("Woman" = "#ccd4dd", "Man" = "#5e6777")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    legend.title = element_text(size = 13),
    legend.text = element_text(size = 11),
    legend.position = "right"
  )

ggsave("gender_collab_year.png", plot =p1_year, width = 10, height = 6)
p1_year
```

### Summary for model 2

```{r}
summary(m2_1)
```

After transformation, intercept is the baseline proportion of BIPOC proportion is approximately 25.2% when all predictors are at their reference levels.

The coefficient on first author gender indicates publications with a woman first author have a lower BIPOC proportion by 1.8%, compared to publications with a man first author, but this effect is not statistically significant.

The coefficient on first author BIPOC indicates that publications with a BIPOC first author have a 17.5% higher BIPOC proportion compared to publications with a White first author, holding other variables constant.

The coefficient on centered publication year suggests for each additional year, the proportion of BIPOC authors in each publication increases by 0.9%.

The coefficient on US affiliation indicates that publications with authors affiliated in the US have a 4.0% higher BIPOC proportion compared to non-US affiliations.

The coefficient on fund suggests whether an publication is funded or not does not significantly affect the proportion of BIPOC authors.

The coefficient on author count suggests indicates that for each additional author from the mean of author number, the BIPOC proportion decreases by 1.1%.

The coefficient on document type suggests Review show no significant difference in the proportion of BIPOC authors compared to Article.

Publications in JoCN have a 6.8% higher BIPOC proportion compared to Brain, and publications in Nature Neuroscience have a 6.7% higher BIPOC proportion compared to Brain.

The coefficient for interaction effect suggests that the combination of a woman first author and a BIPOC first author is associated with a 3.4% lower BIPOC proportion compared to the expected additive effect. 


#### Visualization for model 2

```{r}
# Bar plot for first author gender and race effect on BIPOC proportion
m2_graph <- gamlss(bipoc_prop ~ first_author_gender * first_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

fitted_values <- fitted(m2_graph)

results <- data.frame(
  first_author_gender = data$first_author_gender,
  first_author_bipoc = data$first_author_bipoc,
  affiliation_us = data$affiliation_us,
  fund = data$fund,
  document_type = data$document_type,
  journal = data$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(first_author_gender, first_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p2<- ggplot(predictions_summary,aes(x = factor(first_author_bipoc, levels = c(0, 1), 
                                    labels = c("White", "BIPOC")), 
                     y = mean_pred, 
                     fill = factor(first_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "First Author Race",
    y = "Predicted BIPOC Proportion",
    fill = "First Author Gender",
    title = "Predicted BIPOC Proportion Based on First Author Gender and Race"
  ) +
  scale_fill_manual(values = c("Man" = "#5e6777", "Woman" = "#ccd4dd")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

p2

ggsave("race_collab_bar.png", plot = p2, width = 10, height = 6)
```


```{r}
# Line plot for first author gender and race effect on BIPOC proportion
predictions_summary_year <- results %>%
  group_by(first_author_gender, first_author_bipoc, publication_year = data$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p2_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 linetype = factor(first_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC")),
                 color= factor(first_author_gender, levels = c(1, 0), 
                                labels = c("Woman", "Man")))) +
  geom_line(size = 1.5) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(first_author_gender, levels = c(1, 0), 
                                labels = c("Woman", "Man"))), 
              alpha = 0.07, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted BIPOC Proportion",
    color = "First Author Gender",
    linetype = "First Author Race",
    fill = "First Author Gender",
    title = "Predicted BIPOC Proportion Over Years"
  ) +
  scale_color_manual(values = c("Woman" = "#ccd4dd", "Man" = "#5e6777")) +
  scale_fill_manual(values = c("Woman" = "#ccd4dd", "Man" = "#5e6777")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    legend.title = element_text(size = 13),
    legend.text = element_text(size = 11),
    legend.position = "right"
  )

ggsave("bipoc_collab_year.png", plot =p2_year, width = 10, height = 6)
p2_year
```
### Summary for model 3&4

```{r}
summary(m3_1)
summary(m4_1)
```


```{r}
# Line plot for last author gender and race effect on women proportion

m3_graph <- gamlss(women_prop ~ last_author_gender * last_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

fitted_values <- fitted(m3_graph)

results <- data.frame(
  last_author_gender = data_last$last_author_gender,
  last_author_bipoc = data_last$last_author_bipoc,
  affiliation_us = data_last$affiliation_us,
  fund = data_last$fund,
  document_type = data_last$document_type,
  journal = data_last$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(last_author_gender, last_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p3<- ggplot(predictions_summary, aes(x = factor(last_author_gender, levels = c(0, 1), 
                                    labels = c("Man", "Woman")), 
                     y = mean_pred, 
                     fill = factor(last_author_bipoc, levels = c(0, 1), 
                                   labels = c("White", "BIPOC"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "Last Author Gender",
    y = "Predicted Women Proportion",
    fill = "Last Author Race",
    title = "Predicted Women Proportion Based on Last Author Gender and Race"
  ) +
  scale_fill_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 14),
    legend.position = "top"
  )
p3

ggsave("gender_collab_last_bar.png", plot = p3, width = 10, height = 6)
```

```{r}
# Line plot for last author gender and race effect on women proportion

predictions_summary_year <- results %>%
  group_by(last_author_gender, last_author_bipoc, publication_year = data_last$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p3_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 color = factor(last_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC")),
                 linetype = factor(last_author_gender, levels = c(1, 0), 
                                   labels = c("Woman", "Man")))) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(last_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC"))), 
              alpha = 0.1, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted Women Proportion",
    color = "Last Author Race",
    linetype = "Last Author Gender",
    fill = "Last Author Race",
    title = "Predicted Women Proportion Over Years"
  ) +
  scale_color_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +
  scale_fill_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

ggsave("gender_collab_year_last.png", plot =p3_year, width = 10, height = 6)
p3_year
```


```{r}
# Bar plot for last author gender and race effect on BIPOC proportion

m4_graph <- gamlss(bipoc_prop ~ last_author_gender * last_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

fitted_values <- fitted(m4_graph)

results <- data.frame(
  last_author_gender = data_last$last_author_gender,
  last_author_bipoc = data_last$last_author_bipoc,
  affiliation_us = data_last$affiliation_us,
  fund = data_last$fund,
  document_type = data_last$document_type,
  journal = data_last$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(last_author_gender, last_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p4<- ggplot(predictions_summary,aes(x = factor(last_author_bipoc, levels = c(0, 1), 
                                    labels = c("White", "BIPOC")), 
                     y = mean_pred, 
                     fill = factor(last_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "Last Author Race",
    y = "Predicted BIPOC Proportion",
    fill = "Last Author Gender",
    title = "Predicted BIPOC Proportion Based on Last Author Gender and Race"
  ) +
  scale_fill_manual(values = c("Man" = "#5e6777", "Woman" = "#ccd4dd")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

p4

ggsave("race_collab_last_bar.png", plot = p4, width = 10, height = 6)
```

```{r}
# Line plot for last author gender and race effect on BIPOC proportion

predictions_summary_year <- results %>%
  group_by(last_author_gender, last_author_bipoc, publication_year = data_last$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p4_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 linetype = factor(last_author_bipoc, levels = c(1, 0), 
                                labels = c("BIPOC", "White")),
                 color = factor(last_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman")))) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(last_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC"))), 
              alpha = 0.1, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted BIPOC Proportion",
    color = "Last Author Race",
    linetype = "Last Author Gender",
    fill = "Last Author Race",
    title = "Predicted BIPOC Proportion Over Years"
  ) +
  scale_color_manual(values = c("Man" = "#1e1e1e", "Woman" = "#ccd4dd")) +
  scale_fill_manual(values = c("Man" = "#1e1e1e", "Woman" = "#ccd4dd")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )


ggsave("bipoc_collab_year_last.png", plot =p4_year, width = 10, height = 6)
p4_year
```

