---
title: "diversity"
author: "Shiyu Yang"
date: "2024-11-03"
output: html_document
---
This RMD file is build to explore Shiyu's second research question: Whether women and BIPOC authors collaborate with in-group members and other underrepresented members?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(emmeans)
library(gamlss)
```

# Read data

## Publication-level data
```{r}
publication_data<- read.csv("updating_full_data.csv") 
```

## Author-level data
```{r}
raw_author_data<- read.csv("updating_gender_bipoc_data.csv") 

author_data<- raw_author_data%>% 
  mutate(bipoc = as.factor(bipoc),
         gender = as.factor(gender)) %>% 
  distinct()
```

# Data Wrangling

## Exclude first author in all publications

```{r}
# Exclude first author
author_exclude<- author_data %>% 
  group_by(doi) %>%
  mutate(author_rank = row_number()) %>% 
  filter(author_rank > 1) %>%          
  ungroup() %>%                        
  select(-author_rank)

# Don't exclude
author<- author_data %>% 
  group_by(doi) %>%
  mutate(author_rank = row_number()) %>% 
  filter(author_rank > 1) %>%          
  ungroup() %>%                        
  select(-author_rank)

# Calculate the actual count 
author_prop <- author %>%
  group_by(publication_year, gender, bipoc) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(publication_year) %>%
  mutate(proportion = count / sum(count))

# Calculate women proportion in overall
overall_women_proportion <- sum(author_prop$count[author_prop$gender == 1], na.rm = TRUE) /
  sum(author_prop$count, na.rm = TRUE)

# Calculate BIPOC proportion in overall
overall_bipoc_proportion <- sum(author_prop$count[author_prop$bipoc == 1], na.rm = TRUE) /
  sum(author_prop$count, na.rm = TRUE)
```

The overall_women_proportion represents among all publication from 200

## First author collaboation

```{r}
# Calculate the women and BIPOC proportion after excluding first author
first_data <- author_exclude %>%
  dplyr::select(author_full_names, doi, gender, bipoc) %>% 
  group_by(doi) %>%
  summarize(
    author_counts = n() ,  
    women_prop = mean(gender == "1", na.rm = TRUE),  
    bipoc_prop = mean(bipoc == "1", na.rm = TRUE)
  )

# Filter data
data <- publication_data %>%
  dplyr::filter (overlap_corr_author == "1"|overlap_corr_author == "2") %>% 
  dplyr::select(doi, cited_count,first_author_gender, first_author_bipoc, publication_year, journal, author_count, document_type, fund, affiliation_us,single_author) %>%
  left_join(first_data, by = "doi") %>% 
  dplyr::filter (single_author == "0") %>% 
  mutate(publication_year = 2024 - publication_year) %>% 
  mutate(across(c(single_author,fund,affiliation_us,
                  first_author_bipoc, first_author_gender, document_type, journal), 
                as.factor)) %>% 
  filter(!is.na(first_author_gender), !is.na(first_author_bipoc),
         !is.na(women_prop), !is.na(bipoc_prop),!is.na(author_counts))
  

#colSums(is.na(data)) # Check NAs

# Center data
data$publication_year_c <- data$publication_year - mean(data$publication_year, na.rm = T)
data$author_count_c <- data$author_count - mean(data$author_count, na.rm = T)
```

## Last author collaboration

```{r}
# Calculate the women and BIPOC proportion after excluding last author
last_author_data  <- author_data %>%
  dplyr::select(author_full_names, doi, gender, bipoc) %>%
  group_by(doi) %>%
  slice(1:(n() - 1)) %>%  
  summarize(
    author_counts = n(),
    women_prop = mean(gender == "1", na.rm = TRUE),
    bipoc_prop = mean(bipoc == "1", na.rm = TRUE)
  )

# Filter data
data_last <- publication_data %>%
  dplyr::filter (overlap_corr_author == "1"|overlap_corr_author == "2") %>% 
  dplyr::select(doi, cited_count,last_author_gender, last_author_bipoc, publication_year, journal, author_count, document_type, fund, affiliation_us,single_author) %>%
  left_join(last_author_data, by = "doi") %>% 
  dplyr::filter (single_author == "0") %>% 
  mutate(publication_year = 2024 - publication_year) %>% 
  mutate(across(where(is.character), factor)) %>% 
  mutate(across(c(single_author,fund,affiliation_us,
                  last_author_bipoc, last_author_gender, document_type, journal), 
                as.factor)) %>% 
  filter(!is.na(last_author_gender), !is.na(last_author_bipoc),
         !is.na(women_prop), !is.na(bipoc_prop),!is.na(author_counts))

#colSums(is.na(data_last)) # Check NAs

# Center data
data_last$publication_year_c <- data_last$publication_year - mean(data_last$publication_year, na.rm = T)
data_last$author_count_c <- data_last$author_count - mean(data_last$author_count, na.rm = T)
```

# EDA

## Author gender and BIPOC distribution in overall
```{r}
ggplot(data, aes(x = women_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#7F8993", color = "black") +
  labs(x = "Proportion of Women Authors", y = "Number of Publications") 

ggplot(data, aes(x = bipoc_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#dbc6d9", color = "black") +
  labs(x = "Proportion of BIPOC Authors", y = "Number of Publications") 

ggplot(data_last, aes(x = women_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#7F8993", color = "black") +
  labs(x = "Proportion of Women Authors", y = "Number of Publications") 

ggplot(data_last, aes(x = bipoc_prop)) +
  geom_histogram(binwidth = 0.1, fill = "#dbc6d9", color = "black") +
  labs(x = "Proportion of BIPOC Authors", y = "Number of Publications") 
```
Heavy on tails (0 and 1), so I choose GAM with Beta-inflated distribution or GLM with quasibinomial distribution for data analysis. 

# Model fitting
```{r}
m1_1 <- gamlss(women_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

m2_1 <- gamlss(bipoc_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

m3_1 <- gamlss(women_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

m4_1 <- gamlss(bipoc_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

m1_2 <- glm(women_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data)

m2_2 <- glm(bipoc_prop ~ first_author_gender * first_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data)

m3_2 <- glm(women_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data_last)

m3_2 <- glm(bipoc_prop ~ last_author_gender * last_author_bipoc + 
               publication_year_c + fund + author_count_c + 
               document_type + affiliation_us + journal, 
             family = quasibinomial(link = "logit"), data = data_last)
```
## Model comparison

### plots
```{r}
plot(m1_1) 
plot(m1_2) 

# m1_1 looks better
```
### RMSE with cross-validation
```{r}
set.seed(123) 
k_folds <- 5
folds <- cut(seq(1, nrow(data)), breaks = k_folds, labels = FALSE)

rmse_gamlss <- numeric(k_folds)
rmse_glm <- numeric(k_folds)

# Cross-validation
for (i in 1:k_folds) {
  test_indices <- which(folds == i, arr.ind = TRUE)
  train_data <- data[-test_indices, ]
  test_data <- data[test_indices, ]
  m1 <- gamlss(
    women_prop ~ first_author_gender * first_author_bipoc +
      publication_year_c + fund + author_count_c +
      document_type + affiliation_us + journal,
    family = BEINF,
    data = train_data
  )
  predictions_gamlss <- predict(m1, newdata = test_data, type = "response")
  rmse_gamlss[i] <- sqrt(mean((test_data$women_prop - predictions_gamlss)^2))
  
  m2 <- glm(
    women_prop ~ first_author_gender * first_author_bipoc +
      publication_year_c + fund + author_count_c +
      document_type + affiliation_us + journal,
    family = quasibinomial(link = "logit"),
    data = train_data
  )
  predictions_glm <- predict(m2, newdata = test_data, type = "response")
  rmse_glm[i] <- sqrt(mean((test_data$women_prop - predictions_glm)^2))
}

avg_rmse_gamlss <- mean(rmse_gamlss)
avg_rmse_glm <- mean(rmse_glm)

cat("Average RMSE for GAMLSS model:", avg_rmse_gamlss, "\n")
cat("Average RMSE for GLM model:", avg_rmse_glm, "\n")
```
Although the GLM has lower RMSE, compare to the plot, I will use GAM in the following.


```{r}
summary(m1_1)
summary(m2_1)
```
```{r}
m1_graph <- gamlss(women_prop ~ first_author_gender * first_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

fitted_values <- fitted(m1_graph)

results <- data.frame(
  first_author_gender = data$first_author_gender,
  first_author_bipoc = data$first_author_bipoc,
  affiliation_us = data$affiliation_us,
  fund = data$fund,
  document_type = data$document_type,
  journal = data$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(first_author_gender, first_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p1<- ggplot(predictions_summary, aes(x = factor(first_author_gender, levels = c(0, 1), 
                                    labels = c("Man", "Woman")), 
                     y = mean_pred, 
                     fill = factor(first_author_bipoc, levels = c(0, 1), 
                                   labels = c("White", "BIPOC"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "First Author Gender",
    y = "Predicted Women Proportion",
    fill = "First Author Race",
    title = "Predicted Women Proportion Based on First Author Gender and Race"
  ) +
  scale_fill_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 14),
    legend.position = "top"
  )
p1

ggsave("gender_collab_bar.png", plot = p1, width = 10, height = 6)
```

```{r}
predictions_summary_year <- results %>%
  group_by(first_author_gender, first_author_bipoc, publication_year = data$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p1_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 color = factor(first_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC")),
                 linetype = factor(first_author_gender, levels = c(1, 0), 
                                   labels = c("Woman", "Man")))) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(first_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC"))), 
              alpha = 0.1, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted Women Proportion",
    color = "First Author Race",
    linetype = "First Author Gender",
    fill = "First Author Race",
    title = "Predicted Women Proportion Over Years"
  ) +
  scale_color_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +
  scale_fill_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

ggsave("gender_collab_year.png", plot =p1_year, width = 10, height = 6)
p1_year
```


```{r}
m2_graph <- gamlss(bipoc_prop ~ first_author_gender * first_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data)

fitted_values <- fitted(m2_graph)

results <- data.frame(
  first_author_gender = data$first_author_gender,
  first_author_bipoc = data$first_author_bipoc,
  affiliation_us = data$affiliation_us,
  fund = data$fund,
  document_type = data$document_type,
  journal = data$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(first_author_gender, first_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p2<- ggplot(predictions_summary,aes(x = factor(first_author_bipoc, levels = c(0, 1), 
                                    labels = c("White", "BIPOC")), 
                     y = mean_pred, 
                     fill = factor(first_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "First Author Race",
    y = "Predicted BIPOC Proportion",
    fill = "First Author Gender",
    title = "Predicted BIPOC Proportion Based on First Author Gender and Race"
  ) +
  scale_fill_manual(values = c("Man" = "#5e6777", "Woman" = "#ccd4dd")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

p2

ggsave("race_collab_bar.png", plot = p2, width = 10, height = 6)
```
```{r}
predictions_summary_year <- results %>%
  group_by(first_author_gender, first_author_bipoc, publication_year = data$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p2_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 linetype = factor(first_author_bipoc, levels = c(1, 0), 
                                labels = c("BIPOC", "White")),
                 color= factor(first_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman")))) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(first_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman"))), 
              alpha = 0.1, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted BIPOC Proportion",
    color = "First Author Gender",
    linetype = "First Author Race",
    fill = "First Author Gender",
    title = "Predicted BIPOC Proportion Over Years"
  ) +
  scale_color_manual(values = c("Man" = "#1e1e1e", "Woman" = "#ccd4dd")) +
  scale_fill_manual(values = c("Man" = "#1e1e1e", "Woman" = "#ccd4dd")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

ggsave("bipoc_collab_year.png", plot =p2_year, width = 10, height = 6)
p2_year
```


```{r}
summary(m3_1)
summary(m4_1)
```


```{r}
m3_graph <- gamlss(women_prop ~ last_author_gender * last_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

fitted_values <- fitted(m3_graph)

results <- data.frame(
  last_author_gender = data_last$last_author_gender,
  last_author_bipoc = data_last$last_author_bipoc,
  affiliation_us = data_last$affiliation_us,
  fund = data_last$fund,
  document_type = data_last$document_type,
  journal = data_last$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(last_author_gender, last_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p3<- ggplot(predictions_summary, aes(x = factor(last_author_gender, levels = c(0, 1), 
                                    labels = c("Man", "Woman")), 
                     y = mean_pred, 
                     fill = factor(last_author_bipoc, levels = c(0, 1), 
                                   labels = c("White", "BIPOC"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "Last Author Gender",
    y = "Predicted Women Proportion",
    fill = "Last Author Race",
    title = "Predicted Women Proportion Based on Last Author Gender and Race"
  ) +
  scale_fill_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 14),
    legend.position = "top"
  )
p3

ggsave("gender_collab_last_bar.png", plot = p3, width = 10, height = 6)
```

```{r}
predictions_summary_year <- results %>%
  group_by(last_author_gender, last_author_bipoc, publication_year = data_last$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p3_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 color = factor(last_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC")),
                 linetype = factor(last_author_gender, levels = c(1, 0), 
                                   labels = c("Woman", "Man")))) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(last_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC"))), 
              alpha = 0.1, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted Women Proportion",
    color = "Last Author Race",
    linetype = "Last Author Gender",
    fill = "Last Author Race",
    title = "Predicted Women Proportion Over Years"
  ) +
  scale_color_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +
  scale_fill_manual(values = c("White" = "#7F8993", "BIPOC" = "#dbc6d9")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

ggsave("gender_collab_year_last.png", plot =p3_year, width = 10, height = 6)
p3_year
```


```{r}
m4_graph <- gamlss(bipoc_prop ~ last_author_gender * last_author_bipoc + 
               publication_year + fund + author_count + 
               document_type + affiliation_us + journal, family=BEINF, data=data_last)

fitted_values <- fitted(m4_graph)

results <- data.frame(
  last_author_gender = data_last$last_author_gender,
  last_author_bipoc = data_last$last_author_bipoc,
  affiliation_us = data_last$affiliation_us,
  fund = data_last$fund,
  document_type = data_last$document_type,
  journal = data_last$journal,
  fitted = fitted_values
)

predictions_summary <- results %>%
  group_by(last_author_gender, last_author_bipoc) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p4<- ggplot(predictions_summary,aes(x = factor(last_author_bipoc, levels = c(0, 1), 
                                    labels = c("White", "BIPOC")), 
                     y = mean_pred, 
                     fill = factor(last_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "Last Author Race",
    y = "Predicted BIPOC Proportion",
    fill = "Last Author Gender",
    title = "Predicted BIPOC Proportion Based on Last Author Gender and Race"
  ) +
  scale_fill_manual(values = c("Man" = "#5e6777", "Woman" = "#ccd4dd")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size =12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )

p4

ggsave("race_collab_last_bar.png", plot = p4, width = 10, height = 6)
```
```{r}
predictions_summary_year <- results %>%
  group_by(last_author_gender, last_author_bipoc, publication_year = data_last$publication_year) %>%
  summarise(
    mean_pred = mean(fitted, na.rm = TRUE),
    sd_pred = sd(fitted, na.rm = TRUE),
    n = n()
  )

p4_year <- ggplot(predictions_summary_year, 
             aes(x = publication_year, y = mean_pred, 
                 linetype = factor(last_author_bipoc, levels = c(1, 0), 
                                labels = c("BIPOC", "White")),
                 color = factor(last_author_gender, levels = c(0, 1), 
                                   labels = c("Man", "Woman")))) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_pred - sd_pred, ymax = mean_pred + sd_pred, 
                  fill = factor(last_author_bipoc, levels = c(0, 1), 
                                labels = c("White", "BIPOC"))), 
              alpha = 0.1, color = NA) +
  labs(
    x = "Publication Year",
    y = "Predicted BIPOC Proportion",
    color = "Last Author Race",
    linetype = "Last Author Gender",
    fill = "Last Author Race",
    title = "Predicted BIPOC Proportion Over Years"
  ) +
  scale_color_manual(values = c("Man" = "#1e1e1e", "Woman" = "#ccd4dd")) +
  scale_fill_manual(values = c("Man" = "#1e1e1e", "Woman" = "#ccd4dd")) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5, size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.position = "top"
  )


ggsave("bipoc_collab_year_last.png", plot =p4_year, width = 10, height = 6)
p4_year
```

