---
title: "EDA"
author: "Shiyu Yang"
date: "2024/8/27"
output: html_document
---

# Set up enviromnent

```{r}
options(conflicts.policy = "depends.ok")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_ml.R?raw=true")
tidymodels_conflictRules()

library(cowplot, include.only = c("plot_grid", "theme_half_open"))
library(corrplot, include.only = "corrplot.mixed") 
library(tidyverse) 
library(tidymodels)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_plots.R?raw=true")
```
# Read data and clean

```{r}
raw_data<- read.csv("updating_full_data.csv")

# Remove NAs and mutate class
data<- raw_data %>% 
  dplyr::filter(!is.na(first_author_gender)) %>% 
  dplyr::filter(!is.na(first_author_bipoc)) %>% 
  dplyr::filter(!is.na(last_author_gender)) %>% 
  dplyr::filter(!is.na(last_author_bipoc)) %>% 
  dplyr::filter(!is.na(corresponding_author_bipoc)) %>%  
  dplyr::filter(!is.na(corresponding_author_gender)) %>%  
  dplyr::filter(!is.na(all_bipoc)) %>%   
  dplyr::filter(!is.na(all_white)) %>%  
  dplyr::filter(!is.na(all_men)) %>%   
  dplyr::filter(!is.na(all_women)) %>%  
  mutate(first_author_gender_bipoc = ifelse(first_author_gender_bipoc == 0, "00", 
                                     ifelse(first_author_gender_bipoc == 1, "01", 
                                            as.character(first_author_gender_bipoc))),
         last_author_gender_bipoc = ifelse(last_author_gender_bipoc == 0, "00", 
                                    ifelse(last_author_gender_bipoc == 1, "01", 
                                           as.character(last_author_gender_bipoc))),
      corresponding_author_gender_bipoc = ifelse(corresponding_author_gender_bipoc == 0, "00", 
                                          ifelse(corresponding_author_gender_bipoc == 1, "01", 
                                          as.character(corresponding_author_gender_bipoc)))) %>% 
  mutate(across(where(is.character), factor)) %>% 
  mutate(across(c(single_author, fund, affiliation_dev, affiliation_us,
                  first_author_bipoc, first_author_gender, first_author_gender_bipoc,
                  last_author_gender,last_author_bipoc, last_author_gender_bipoc,
                  corresponding_author_gender, corresponding_author_bipoc,
                  corresponding_author_gender_bipoc,  
                  overlap_corr_author,all_men,all_women,all_white,all_bipoc), 
                as.factor)) 
```

# Check missing values and classes

```{r}
data %>% skim_all()
```

# Univariant Distribution

## Numeric variables
```{r}
data %>% 
  select(where(is.numeric)) %>% 
  names() %>% 
  map(\(name) plot_box_violin(df = data, x = name)) %>% 
  plot_grid(plotlist = ., ncol = 2)
```

# Further check over-dispersed in counts which is our DV
```{r}
mean(data$cited_count)
var(data$cited_count)
mean(data$cited_count == 0)

ggplot(data, aes(x = cited_count)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Density Plot of Count Data", x = "Count", y = "Density") +
  theme_minimal()
```


## Categorical variables
### Article characteristic
```{r}
data %>% plot_bar("document_type")
data %>% plot_bar("fund")
data %>% plot_bar("country")
data %>% plot_bar("affiliation_con")
data %>% plot_bar("affiliation_dev")
data %>% plot_bar("affiliation_us")
data %>% plot_bar("single_author")
data %>% plot_bar("journal")
```
document_type: majority of publications in this dataset are articles.

fund: majority of publication in current data is funded.

country: USA affliation is the leading country publish in neuroscience in current data.

affiliation_con: North American and Europe affilation are the leading continent publish in neuroscience in current data.

affiliation_dev: Majority of publications in this dataset came from affiliations from developed economics.

affiliation_us: publications from US and non-US countries are relative balanced in this dataset.

single_author: most of the publication were published with multiple authors.

journal: distribution of publications from each journal.


### Gender and Race
```{r}
data %>% plot_bar("first_author_bipoc")
data %>% plot_bar("first_author_gender")
data %>% plot_bar("first_author_gender_bipoc")
data %>% plot_bar("last_author_bipoc")
data %>% plot_bar("last_author_gender")
data %>% plot_bar("last_author_gender_bipoc")
data %>% plot_bar("corresponding_author_bipoc")
data %>% plot_bar("corresponding_author_gender")
data %>% plot_bar("corresponding_author_gender_bipoc")
data %>% plot_bar("fl_gender")
data %>% plot_bar("fl_bipoc")
data %>% plot_bar("all_men")
data %>% plot_bar("all_women")
data %>% plot_bar("all_white")
data %>% plot_bar("all_bipoc")
```
Women and BIPOC authors are less in the publication as first, last, and corresponding authors.

# Bivariate Relationships

## Numeric variables
```{r}
data %>% 
  select(where(is.numeric) &!cited_count) %>% 
  names() %>% 
  map(\(name) plot_scatter(df = data, x = name, y = "cited_count")) %>% 
  plot_grid(plotlist = ., ncol = 2)
```
The older and more authors in publication positively associate with more cited counts.

```{r}
data %>% 
  select(where(is.numeric)) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  corrplot::corrplot.mixed()
```

## Categorical variables

### Article characteristic
```{r}
data %>% plot_grouped_box_violin ("document_type", "cited_count")
data %>% plot_grouped_box_violin ("fund", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_con", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_dev", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_us", "cited_count")
data %>% plot_grouped_box_violin ("journal", "cited_count")
```

### Gender and Race
```{r}
data %>% plot_grouped_box_violin ("first_author_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("first_author_gender", "cited_count")
data %>% plot_grouped_box_violin ("first_author_gender_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("last_author_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("last_author_gender", "cited_count")
data %>% plot_grouped_box_violin ("last_author_gender_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("corresponding_author_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("corresponding_author_gender", "cited_count")
data %>% plot_grouped_box_violin ("corresponding_author_gender_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("fl_gender", "cited_count")
data %>% plot_grouped_box_violin ("fl_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("all_men", "cited_count")
data %>% plot_grouped_box_violin ("all_women", "cited_count")
data %>% plot_grouped_box_violin ("all_white", "cited_count")
data %>% plot_grouped_box_violin ("all_bipoc", "cited_count")
```