---
title: "EDA"
author: "Shiyu Yang"
date: "2024/8/27"
output: html_document
---

```{r}
options(conflicts.policy = "depends.ok")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_ml.R?raw=true")
tidymodels_conflictRules()

library(cowplot, include.only = c("plot_grid", "theme_half_open"))
library(corrplot, include.only = "corrplot.mixed") 
library(tidyverse) 
library(tidymodels)
library(ggplot2)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_plots.R?raw=true")
```

```{r}
raw_data<- read.csv("updating_cleaned_reference.csv")

data<- raw_data %>% 
  dplyr::filter(!is.na(first_author_gender)) %>% 
  dplyr::filter(!is.na(first_author_bipoc)) %>% 
  dplyr::filter(!is.na(last_author_gender)) %>% 
  dplyr::filter(!is.na(last_author_bipoc)) %>% 
  dplyr::filter(!is.na(corresponding_author_bipoc)) %>%   
  dplyr::filter(!is.na(all_bipoc)) %>%   
  dplyr::filter(!is.na(all_white)) %>%  
  dplyr::filter(!is.na(all_men)) %>%   
  dplyr::filter(!is.na(all_women)) %>%  
  dplyr::filter(!is.na(doi)) %>%
  mutate(
    first_author_gender_bipoc = ifelse(first_author_gender_bipoc == 0, "00", 
                                       ifelse(first_author_gender_bipoc == 1, "01", as.character(first_author_gender_bipoc))),
    last_author_gender_bipoc = ifelse(last_author_gender_bipoc == 0, "00", 
                                      ifelse(last_author_gender_bipoc == 1, "01", as.character(last_author_gender_bipoc))),
    corresponding_author_gender_bipoc = ifelse(corresponding_author_gender_bipoc == 0, "00", 
                                               ifelse(corresponding_author_gender_bipoc == 1, "01", as.character(corresponding_author_gender_bipoc)))
  ) %>% 
  mutate(across(where(is.character), factor)) %>% 
  mutate(across(c(single_author, fund, affiliation_dev, affiliation_us,
                  first_author_bipoc, first_author_gender, first_author_gender_bipoc,
                  last_author_gender,last_author_bipoc, last_author_gender_bipoc,
                  corresponding_author_gender,
                  corresponding_author_bipoc, corresponding_author_gender_bipoc,
                  all_men,all_women,all_white,all_bipoc), 
                as.factor))  %>% 
  glimpse()
```

```{r}
data %>% skim_all()
```

# Univariant Distribution

## Numeric variables
```{r}
data %>% 
  select(where(is.numeric)) %>% 
  names() %>% 
  map(\(name) plot_box_violin(df = data, x = name)) %>% 
  plot_grid(plotlist = ., ncol = 2)
```

## Categorical variables
### Article characteristic
```{r}
data %>% plot_bar("document_type")
data %>% plot_bar("fund")
data %>% plot_bar("country")
data %>% plot_bar("affiliation_con")
data %>% plot_bar("affiliation_dev")
data %>% plot_bar("affiliation_us")
data %>% plot_bar("journal")
```

### Gender and Race
```{r}
data %>% plot_bar("first_author_bipoc")
data %>% plot_bar("first_author_gender")
data %>% plot_bar("first_author_gender_bipoc")
data %>% plot_bar("last_author_bipoc")
data %>% plot_bar("last_author_gender")
data %>% plot_bar("last_author_gender_bipoc")
data %>% plot_bar("corresponding_author_bipoc")
data %>% plot_bar("corresponding_author_gender")
data %>% plot_bar("corresponding_author_gender_bipoc")
data %>% plot_bar("fl_gender")
data %>% plot_bar("fl_bipoc")
data %>% plot_bar("all_men")
data %>% plot_bar("all_women")
data %>% plot_bar("all_white")
data %>% plot_bar("all_bipoc")
```

# Bivariate Relationships

## Numeric variables
```{r}
data %>% 
  select(where(is.numeric) &!cited_count) %>% 
  names() %>% 
  map(\(name) plot_scatter(df = data, x = name, y = "cited_count")) %>% 
  plot_grid(plotlist = ., ncol = 2)
```
Female ratio and reference_year has negative correlation with cited_count

```{r}
data %>% 
  select(where(is.numeric)) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  corrplot::corrplot.mixed()
```

## Categorical variables

### Article characteristic
```{r}
data %>% plot_grouped_box_violin ("document_type", "cited_count")
data %>% plot_grouped_box_violin ("fund", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_con", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_dev", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_us", "cited_count")
```

### first_author_gender_bipoc
```{r}
data %>% plot_grouped_box_violin ("document_type", "cited_count")
data %>% plot_grouped_box_violin ("fund", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_con", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_dev", "cited_count")
data %>% plot_grouped_box_violin ("affiliation_us", "cited_count")
data %>% plot_grouped_box_violin ("journal", "cited_count")
```

### Gender and Race
```{r}
data %>% plot_grouped_box_violin ("first_author_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("first_author_gender", "cited_count")
data %>% plot_grouped_box_violin ("first_author_gender_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("last_author_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("last_author_gender", "cited_count")
data %>% plot_grouped_box_violin ("last_author_gender_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("corresponding_author_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("corresponding_author_gender", "cited_count")
data %>% plot_grouped_box_violin ("corresponding_author_gender_bipoc", "cited_count")
data %>% plot_grouped_box_violin ("fl_gender", "cited_count")
data %>% plot_grouped_box_violin ("fl_bipoc", "cited_count")
```
More skewed in white and male author papers

```{r}
ggplot(data, aes(x = author_count, fill = first_author_gender_bipoc)) + 
  geom_density(alpha = 0.5, adjust = 3) + 
  facet_wrap(~ first_author_gender_bipoc)

ggplot(data, aes(x = publication_year, fill = first_author_gender_bipoc)) + 
  geom_density(alpha = 0.5) + 
  facet_wrap(~ first_author_gender_bipoc)

ggplot(data, aes(x = reference_year, fill = first_author_gender_bipoc)) + 
  geom_density(alpha = 0.5) + 
  facet_wrap(~ first_author_gender_bipoc)

ggplot(data, aes(x = woman_ratio, fill = first_author_gender_bipoc)) + 
  geom_density(alpha = 0.5) + 
  facet_wrap(~ first_author_gender_bipoc)
```
first_author_gender_bipoc and author_count has non-linear relationship
