---
title: "visualization"
author: "Shiyu Yang"
date: "2024-11-13"
output: html_document
---
This Rmd file is for visualization of author proportion and Shiyu's research question 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(ggplot2)
library(ggsignif)
library(viridis)
```

# Read data and clean

```{r}
# Read publication data
raw_data<- read.csv("updating_full_data.csv")

# Removed NA in authors, corrected the format of gender_bipoc, correct factor categorization
data<- raw_data %>% 
  dplyr::filter(!is.na(first_author_gender)) %>% 
  dplyr::filter(!is.na(first_author_bipoc)) %>% 
  dplyr::filter(!is.na(last_author_gender)) %>% 
  dplyr::filter(!is.na(last_author_bipoc)) %>% 
  dplyr::filter(!is.na(corresponding_author_bipoc)) %>%   
  dplyr::filter(!is.na(corresponding_author_gender)) %>% 
  dplyr::filter(!is.na(all_bipoc)) %>%   
  dplyr::filter(!is.na(all_white)) %>%  
  dplyr::filter(!is.na(all_men)) %>%   
  dplyr::filter(!is.na(all_women)) %>%  
  mutate(first_author_gender_bipoc = 
           ifelse(first_author_gender_bipoc == 0, "00", 
           ifelse(first_author_gender_bipoc == 1, "01",  
                  as.character(first_author_gender_bipoc))),
         last_author_gender_bipoc = 
           ifelse(last_author_gender_bipoc == 0, "00", 
           ifelse(last_author_gender_bipoc == 1, "01", 
                  as.character(last_author_gender_bipoc))),
         corresponding_author_gender_bipoc = 
           ifelse(corresponding_author_gender_bipoc == 0, "00", 
           ifelse(corresponding_author_gender_bipoc == 1, "01", 
                  as.character(corresponding_author_gender_bipoc)))) %>% 
  mutate(across(where(is.character), factor)) %>% 
  mutate(across(c(single_author, fund, affiliation_dev, affiliation_us,
                  first_author_bipoc, first_author_gender, first_author_gender_bipoc,
                  last_author_gender,last_author_bipoc, last_author_gender_bipoc,
                  corresponding_author_gender, corresponding_author_bipoc, 
                  corresponding_author_gender_bipoc, 
                  all_men,all_women,all_white,all_bipoc, overlap_corr_author), 
                as.factor))  

# Centered continues factors
data$publication_year_c <- data$publication_year - mean(data$publication_year, na.rm = T)
data$author_count_c <- data$author_count - mean(data$author_count, na.rm = T)

# Recode the publication year in data for future plot
data<- data %>% 
  mutate(publication_year = 2024 - publication_year) 

# Filtered out no overlap in corresponding author and first/last author (3% in this dataset)
overlap_data<- data %>% dplyr::filter (overlap_corr_author == "1"|overlap_corr_author == "2")

# Removed single author publication
overlap_data<- overlap_data %>%
  dplyr::filter (single_author == "0")
```

```{r}
# Read author data
author <- read.csv ("updating_gender_bipoc_data.csv") %>% 
  dplyr::select(author_full_names, publication_year, gender, bipoc) %>% 
  na.omit()

# Calculate the proportion for each group author across years
author_prop <- author %>%
  group_by(publication_year, gender, bipoc) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(publication_year) %>%
  mutate(proportion = count / sum(count))
```


# Visualization

## Proportion of Authors Appearance in Neuroscience Publications Across Years

```{r}
p1<- ggplot(author_prop, aes(x = publication_year, y = proportion, fill = interaction(gender, bipoc))) +
  geom_area(alpha = 0.9) +
  labs(title = "Proportion of Authors in Neuroscience Publication Across Years",
       x = "Publication Year",
       y = "Proportion of Authors",
       fill = "Author Gender & Race") +
  scale_fill_manual(values = c("#e6e6f0", "#dbc6d9", "#9f6693", "#4f3e6a"),
                    labels = c("White Man", "BIPOC Man", "White Woman", "BIPOC Woman")) +
  scale_y_continuous(labels = scales::percent_format(),position = "right") +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5),
    legend.title = element_text(size = 13),
    legend.text = element_text(size = 13),
    legend.position = "left"
  )

p1
ggsave("proportion_area_plot.png", plot = p1, width = 10, height = 6)
```

## Proportion of First Authors Appearance in Neuroscience Publications Across Years

```{r}
first_author_year <- data %>%
  filter(!is.na(first_author_bipoc) & !is.na(first_author_gender)) %>%
  group_by(publication_year, first_author_bipoc, first_author_gender) %>%
  summarize(count = n(), .groups = 'drop') %>%
  group_by(publication_year) %>%
  mutate(proportion = count / sum(count)) %>%  # Calculate proportion for each category
  mutate(
    bipoc_label = case_when(
      first_author_bipoc == 1 ~ "BIPOC",
      first_author_bipoc == 0 ~ "White"
    ),
    gender_label = case_when(
      first_author_gender == 1 ~ "Woman",
      first_author_gender == 0 ~ "Man"
    ),
    label = paste(bipoc_label, gender_label) 
  )%>%
  mutate(label = factor(label, levels = c("White Man", "BIPOC Man", "White Woman","BIPOC Woman"))) 

custom_colors <- c(
  "White Man" = "#e6e6f0",    
  "White Woman" = "#9f6693",  
  "BIPOC Man" = "#dbc6d9",      
  "BIPOC Woman" = "#4f3e6a"     
)

p2<- ggplot(first_author_year, aes(x = publication_year, y = proportion, fill = label)) +
  geom_area(alpha = 0.9) +  
  labs(x = "Publication Year", y = "Proportion of Authors", fill = "Race & Gender", color = "Race & Gender", title = "Proportions of First Authors Over the Years") +
  theme_bw() +
  scale_fill_manual(values = custom_colors) +
  theme(legend.position = "right",
    text = element_text(size = 14) ,
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
    legend.text = element_text(size = 13)) 

ggsave("prop_firstauthor_plot.png", plot = p2, width = 10, height = 6)

p2
```

## Proportion of Last Authors Appearance in Neuroscience Publications Across Years

```{r}
last_author_year <- data %>%
  filter(!is.na(last_author_bipoc) & !is.na(last_author_gender)) %>%
  group_by(publication_year, last_author_bipoc, last_author_gender) %>%
  summarize(count = n(), .groups = 'drop') %>%
  group_by(publication_year) %>%
  mutate(proportion = count / sum(count)) %>%  
  mutate(
    bipoc_label = case_when(
      last_author_bipoc == 1 ~ "BIPOC",
      last_author_bipoc == 0 ~ "White"
    ),
    gender_label = case_when(
      last_author_gender == 1 ~ "Woman",
      last_author_gender == 0 ~ "Man"
    ),
    label = paste(bipoc_label, gender_label) 
  )%>%
  mutate(label = factor(label, levels = c("White Man", "BIPOC Man", "White Woman","BIPOC Woman"))) 

custom_colors <- c(
  "White Man" = "#e6e6f0",    
  "White Woman" = "#9f6693",  
  "BIPOC Man" = "#dbc6d9",      
  "BIPOC Woman" = "#4f3e6a"       
)

p3<-ggplot(last_author_year, aes(x = publication_year, y = proportion, fill = label)) +
  geom_area(alpha = 0.9, position = "fill") +  
  labs(x = "Publication Year", y = "Proportion of Authors", fill = "Race & Gender", color = "Race & Gender", title = "Proportions of Last Authors Over the Years") +
  theme_bw() +
  scale_fill_manual(values = custom_colors) +
  theme(legend.position = "right",
    text = element_text(size = 14) ,
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
    legend.text = element_text(size = 13)) 

ggsave("prop_lastauthor_plot.png", plot = p3, width = 10, height = 6)

p3
```
## Proportion of Corresponding Authors Appearance in Neuroscience Publications Across Years

```{r}
corresponding_author_year <- data %>%
  filter(!is.na(corresponding_author_bipoc) & !is.na(corresponding_author_gender)) %>%
  group_by(publication_year, corresponding_author_bipoc, corresponding_author_gender) %>%
  summarize(count = n(), .groups = 'drop') %>%
  group_by(publication_year) %>%
  mutate(proportion = count / sum(count)) %>% 
  mutate(
    bipoc_label = case_when(
      corresponding_author_bipoc == 1 ~ "BIPOC",
      corresponding_author_bipoc == 0 ~ "White"
    ),
    gender_label = case_when(
      corresponding_author_gender == 1 ~ "Woman",
      corresponding_author_gender == 0 ~ "Man"
    ),
    label = paste(bipoc_label, gender_label) 
  )%>%
  mutate(label = factor(label, levels = c("White Man", "BIPOC Man", "White Woman","BIPOC Woman"))) 

custom_colors <- c(
  "White Man" = "#e6e6f0",    
  "White Woman" = "#9f6693",  
  "BIPOC Man" = "#dbc6d9",      
  "BIPOC Woman" = "#4f3e6a"      
)

p4<- ggplot(corresponding_author_year, aes(x = publication_year, y = proportion, fill = label)) +
  geom_area(alpha = 0.9, position = "fill") +  
  labs(x = "Publication Year", y = "Proportion of Authors", fill = "Race & Gender", color = "Race&Gender", title = "Proportions of Corresponding Authors Over the Years") +
    theme_bw() +
  scale_fill_manual(values = custom_colors) +
  theme(legend.position = "right",
    text = element_text(size = 14) ,
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
    legend.text = element_text(size = 13)) 

ggsave("prop_corrauthor_plot.png", plot = p4, width = 10, height = 6)

p4
```



```{r}
m4 <- glm.nb(cited_count ~ first_author_gender * first_author_bipoc + last_author_gender * last_author_bipoc + publication_year + affiliation_us + fund + author_count + journal + document_type, data = overlap_data)

new_data <- expand.grid(
  first_author_gender = unique(overlap_data$first_author_gender),
  last_author_gender = unique(overlap_data$last_author_gender),
  first_author_bipoc = unique(overlap_data$first_author_bipoc),
  last_author_bipoc = unique(overlap_data$last_author_bipoc),
  affiliation_us = unique(overlap_data$affiliation_us),
  publication_year = mean(overlap_data$publication_year, na.rm = T),
  fund = unique(overlap_data$fund),
  document_type = unique(overlap_data$document_type),
  author_count =mean(overlap_data$author_count, na.rm = T),
  journal = unique(overlap_data$journal)
)

predictions <- predict(m4, newdata = new_data, type = "response", se.fit = TRUE)
new_data$cited_count_pred <- predictions$fit
new_data$se <- predictions$se.fit

data_grouped <- new_data %>%
  group_by(first_author_gender, first_author_bipoc) %>%
  summarise(
    cited_count_pred = mean(cited_count_pred),
    se = mean(se),
    .groups = 'drop'
  )

p5<- ggplot(data_grouped, aes(x = factor(first_author_bipoc, levels = c(0, 1), 
                                         labels = c("White", "BIPOC")), 
                     y = cited_count_pred, 
                     fill = factor(first_author_gender, levels = c(0, 1), labels = c("Men", "Women"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = cited_count_pred - se, ymax = cited_count_pred + se), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "First Author Race",
    y = "Predicted Cited Count",
    fill = "First Author Gender",
    title = "Predicted Cited Count Based on First Author Gender and Race"
  ) +
  scale_fill_manual(values = c("Men" = "#5e6777", "Women" = "#ccd4dd")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 14),
    legend.position = "top"
  )

p5

ggsave("FL_bar_plot.png", plot = p5, width = 10, height = 6)
```



```{r}
m6 <- glm.nb(cited_count ~ all_women * all_bipoc + publication_year + affiliation_us + fund+ author_count + journal + document_type, data = overlap_data)

new_data <- expand.grid(
  all_women = unique(overlap_data$all_women),
  all_bipoc = unique(overlap_data$all_bipoc),
  affiliation_us = unique(overlap_data$affiliation_us),
  publication_year = mean(overlap_data$publication_year, na.rm = T),
  fund = unique(overlap_data$fund),
  author_count =mean(overlap_data$author_count, na.rm = T),
  document_type = unique(overlap_data$document_type),
  journal = unique(overlap_data$journal)
)

predictions <- predict(m6, newdata = new_data, type = "response", se.fit = TRUE)
new_data$cited_count_pred <- predictions$fit
new_data$se <- predictions$se.fit

data_grouped <- new_data %>%
  group_by(all_women, all_bipoc) %>%
  summarise(
    cited_count_pred = mean(cited_count_pred),
    se = mean(se)
  )

p6<- ggplot(data_grouped, aes(x = factor(all_bipoc, levels = c(0, 1), 
                                         labels = c("Not All BIPOC", "All BIPOC")), 
                          y = cited_count_pred, 
                          fill = factor(all_women, levels = c(0, 1), labels = c("Not All Women", "All Women")))) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = cited_count_pred - se, ymax = cited_count_pred + se), 
                position = position_dodge(width = 0.9), width = 0.25) +

  labs(
    x = "BIPOC Representation",
    y = "Predicted Cited Count",
    fill = "Women Representation",
    title = "Predicted Cited Count Based on Women and BIPOC authors"
  ) +
  scale_fill_manual(values = c("Not All Women" = "#e6e6f0", "All Women" = "#9f6693")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 14),
        legend.position = "top"
  )


p6
ggsave("allwb_bar_plot.png", plot = p6, width = 10, height = 6)
```

```{r}
m2 <-  glm.nb(cited_count ~ last_author_bipoc * last_author_gender+ publication_year + affiliation_us + fund + document_type + author_count + journal, data = overlap_data)

new_data <- expand.grid(
  last_author_bipoc = unique(data$last_author_bipoc),
  last_author_gender = unique(data$last_author_gender),
  affiliation_us = unique(data$affiliation_us),
  publication_year = mean(data$publication_year, na.rm = T),
  fund = unique(data$fund),
  author_count =mean(data$author_count, na.rm = T),
  document_type = unique(data$document_type),
  journal = unique(data$journal)
)

predictions <- predict(m2, newdata = new_data, type = "response", se.fit = TRUE)
new_data$cited_count_pred <- predictions$fit
new_data$se <- predictions$se.fit

data_grouped <- new_data %>%
  group_by(last_author_bipoc, last_author_gender) %>%
  summarise(
    cited_count_pred = mean(cited_count_pred),
    se = mean(se)
  )

p7<-ggplot(data_grouped, aes(x = factor(last_author_bipoc, levels = c(0, 1), labels = c("White", "BIPOC")), 
                     y = cited_count_pred, 
                     fill = factor(last_author_gender, levels = c(0, 1), labels = c("Men", "Women"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = cited_count_pred - se, ymax = cited_count_pred + se), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "Race",
    y = "Predicted Cited Count",
    fill = "Gender",
    title = "Last Author Gender and Race vs. Citation Count"
  ) +
  scale_fill_manual(values = c("Men" = "#5e6777", "Women" = "#ccd4dd")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )
p7
ggsave("last_bar_plot.png", plot = p7, width = 10, height = 6)
```


```{r}
m3 <-  glm.nb(cited_count ~ corresponding_author_bipoc * corresponding_author_gender + publication_year + affiliation_us + fund + author_count + journal + document_type, data = overlap_data)
new_data <- expand.grid(
  corresponding_author_bipoc = unique(overlap_data$corresponding_author_bipoc),
  corresponding_author_gender = unique(overlap_data$corresponding_author_gender),
  affiliation_us = unique(overlap_data$affiliation_us),
  publication_year = mean(overlap_data$publication_year, na.rm = T),
  fund = unique(overlap_data$fund),
  author_count =mean(overlap_data$author_count, na.rm = T),
  document_type = unique(data$document_type),
  journal = unique(overlap_data$journal)
)

predictions <- predict(m3, newdata = new_data, type = "response", se.fit = TRUE)
new_data$cited_count_pred <- predictions$fit
new_data$se <- predictions$se.fit

data_grouped <- new_data %>%
  group_by(corresponding_author_bipoc, corresponding_author_gender) %>%
  summarise(
    cited_count_pred = mean(cited_count_pred),
    se = mean(se)
  )

p8<-ggplot(data_grouped, aes(x = factor(corresponding_author_bipoc, levels = c(0, 1), labels = c("White", "BIPOC")), 
                     y = cited_count_pred, 
                     fill = factor(corresponding_author_gender, levels = c(0, 1), labels = c("Men", "Women"))))+
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = cited_count_pred - se, ymax = cited_count_pred + se), 
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(
    x = "Race",
    y = "Predicted Cited Count",
    fill = "Gender",
    title = "Corresponding Author Gender and Race vs. Citation Count"
  ) +
  scale_fill_manual(values = c("Men" = "#5e6777", "Women" = "#ccd4dd")) +  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(hjust = 0.5),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

p8
ggsave("corr_bar_plot.png", plot = p8, width = 10, height = 6)
```