---
title: "name_prediction"
author: "Shiyu Yang"
date: "2024-11-05"
output: html_document
---

# This is the Step 3 in Data Clean
Before running code in this file, upload name lists csv files into genderize.io for gender prediction with selecting first name, and in Columns to add select gender and probability. Save the output with the format of prediced_xxx_gender.csv

```{r setup, include=FALSE}
library(tidyverse)
library(wru)
```

# Read in Predicted Data in gender
```{r}
raw_jocn<- read.csv("predicted_jocn_gender.csv") %>% 
  janitor::clean_names() %>%
  select(-x)

raw_nature_neuro<- read.csv("predicted_nature_neuro_gender.csv") %>% 
  janitor::clean_names() %>%
  select(-x)

raw_brain<- read.csv("predicted_brain_gender.csv") %>% 
  janitor::clean_names() %>%
  select(-x)

jocn<- read.csv("jocn_name_list.csv") %>% 
  janitor::clean_names() %>%
  select(-x)

nature_neuro<- read.csv("nature_neuro_name_list.csv") %>% 
  janitor::clean_names() %>%
  select(-x)

brain<- read.csv("brain_name_list.csv") %>% 
  janitor::clean_names() %>%
  select(-x)
```

# Recode gender probability with threshold of .7
```{r}
jocn_gender<- raw_jocn %>%
  mutate(gender = case_when(
    gender == "male" & gender_probability < 0.7 ~ NA,
    gender == "female" & gender_probability < 0.7 ~ NA,
    gender == 'unknown' ~ NA,
    TRUE ~ gender
  )) %>% 
  select(-gender_probability) %>% 
  mutate(gender = recode(gender, "female" = "1", "male" = "0"))

nature_neuro_gender<- raw_nature_neuro %>%
  mutate(gender = case_when(
    gender == "male" & gender_probability < 0.7 ~ NA,
    gender == "female" & gender_probability < 0.7 ~ NA,
    gender == 'unknown' ~ NA,
    TRUE ~ gender
  )) %>% 
  select(-gender_probability) %>% 
  mutate(gender = recode(gender, "female" = "1", "male" = "0"))

brain_gender<- raw_brain %>%
  mutate(gender = case_when(
    gender == "male" & gender_probability < 0.7 ~ NA,
    gender == "female" & gender_probability < 0.7 ~ NA,
    gender == 'unknown' ~ NA,
    TRUE ~ gender
  )) %>% 
  select(-gender_probability) %>% 
  mutate(gender = recode(gender, "female" = "1", "male" = "0"))
```

# Predict race based on last name and merge with gender data
```{r}
jocn <- jocn %>% rename(surname = last_name)

# Predict race
race_jocn <- predict_race(raw_jocn, surname.only = TRUE)

# Recode probability under 70% as NA
predicted_jocn <- race_jocn %>%
  mutate(max_race = case_when(
    pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) < 0.7 ~ "unknown",
    pred.whi == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "white",
    pred.bla == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "black",
    pred.his == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "hispanic",
    pred.asi == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "asian",
    pred.oth == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "unknown"
  )) %>% 
  rename(last_name = surname)

# Recode White as 0, BIPOC as 1
predicted_jocn$bipoc <- ifelse(predicted_jocn$max_race %in% c("hispanic", "black", "asian"), 1,
                        ifelse(predicted_jocn$max_race == "white", 0, NA)) 

# Remove unnecessary columns
predicted_jocn <-predicted_jocn %>% 
  select(-pred.whi, -pred.bla, -pred.his, -pred.asi, -pred.oth, -max_race) %>%
  left_join(jocn_gender, by = "first_name")%>% 
  mutate(bipoc = as.character(bipoc))

nature_neuro <- nature_neuro %>% rename(surname = last_name)

# Predict race
race_nature_neuro <- predict_race(nature_neuro, surname.only = TRUE)

# Recode probability under 70% as NA
predicted_nature_neuro <- race_nature_neuro %>%
  mutate(max_race = case_when(
    pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) < 0.7 ~ "unknown",
    pred.whi == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "white",
    pred.bla == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "black",
    pred.his == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "hispanic",
    pred.asi == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "asian",
    pred.oth == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "unknown"
  )) %>% 
  rename(last_name = surname)

# Recode White as 0, BIPOC as 1
predicted_nature_neuro$bipoc <- ifelse(predicted_nature_neuro$max_race %in% c("hispanic", "black", "asian"), 1,
                        ifelse(predicted_nature_neuro$max_race == "white", 0, NA)) 

# Remove unnecessary columns
predicted_nature_neuro <-predicted_nature_neuro %>% 
  select(-pred.whi, -pred.bla, -pred.his, -pred.asi, -pred.oth, -max_race) %>%
  left_join(nature_neuro_gender, by = "first_name") %>% 
  mutate(bipoc = as.character(bipoc))

brain <- brain %>% rename(surname = last_name)

# Predict race
race_brain <- predict_race(brain, surname.only = TRUE)

# Recode probability under 70% as NA
predicted_brain <- race_brain %>%
  mutate(max_race = case_when(
    pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) < 0.7 ~ "unknown",
    pred.whi == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "white",
    pred.bla == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "black",
    pred.his == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "hispanic",
    pred.asi == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "asian",
    pred.oth == pmax(pred.whi, pred.bla, pred.his, pred.asi, pred.oth) ~ "unknown"
  )) %>% 
  rename(last_name = surname)

# Recode White as 0, BIPOC as 1
predicted_brain$bipoc <- ifelse(predicted_brain$max_race %in% c("hispanic", "black", "asian"), 1,
                        ifelse(predicted_brain$max_race == "white", 0, NA)) 

# Remove unnecessary columns
predicted_brain <-predicted_brain %>% 
  select(-pred.whi, -pred.bla, -pred.his, -pred.asi, -pred.oth, -max_race) %>%
  left_join(brain_gender, by = "first_name")%>% 
  mutate(bipoc = as.character(bipoc))
```


# Output missing data and manual label
```{r}
missing_jocn <- predicted_jocn %>% 
  filter(is.na(bipoc)|is.na(gender)) 

missing_nature_neuro <- predicted_nature_neuro %>% 
  filter(is.na(bipoc)|is.na(gender)) 

missing_brain <- predicted_brain %>% 
  filter(is.na(bipoc)|is.na(gender)) 

#write.csv(missing_value, file = "missing_value_jocn.csv")
#write.csv(missing_value, file = "missing_value_nature_neuro.csv")
#write.csv(missing_value, file = "missing_value_brain.csv")
# Rename these file after cleaning to "cleaned_missing_value_xxx.csv"
```

# Merge Manual Labeled Data
```{r}
# Read in manual labeled data in JoCN
labeled_jocn<- read.csv("cleaned_missing_value_jocn.csv") %>% 
  mutate(gender = case_when(
    gender == '' ~ NA,
    TRUE ~ gender),
    bipoc = as.character(bipoc)) %>% 
  select(-first_name,-last_name)

# Merge labeled data into full name list
final_jocn<- predicted_jocn %>% 
  left_join(labeled_jocn, by = "full_name") %>% 
  mutate(gender = coalesce(gender.x, gender.y),
         bipoc  = coalesce(bipoc.x, bipoc.y)) %>%
  select(-gender.x, -gender.y,-bipoc.x, -bipoc.y)

# Recode any NA from merging due to full name unmatching
final_jocn <- final_njocn %>%
  group_by(first_name, last_name) %>%
  mutate(bipoc = ifelse(is.na(bipoc), first(na.omit(bipoc)), bipoc)) %>%
  ungroup()

final_jocn<- final_jocn %>% 
  distinct() 

# Read in manual labeled data in Nature Neuroscience
labeled_nature_neuro<- read.csv("cleaned_missing_value_nature_neuro.csv") %>% 
  mutate(gender = case_when(
    gender == '' ~ NA,
    TRUE ~ gender),
  bipoc = as.character(bipoc)) %>% 
  select(-first_name,-last_name)

# Merge labeled data into full name list
final_nature_neuroscience<- predicted_nature_neuro %>% 
  left_join(labeled_nature_neuro, by = "full_name") %>% 
  mutate(gender = coalesce(gender.x, gender.y),
         bipoc  = coalesce(bipoc.x, bipoc.y)) %>%
  select(-gender.x, -gender.y,-bipoc.x, -bipoc.y)

# Recode any NA from merging due to full name unmatching
final_nature_neuroscience <- final_nature_neuroscience %>%
  group_by(first_name, last_name) %>%
  mutate(bipoc = ifelse(is.na(bipoc), first(na.omit(bipoc)), bipoc)) %>%
  ungroup()

# Manual clean for some author name due to formatting in name (e.g. with or without initials)
final_nature_neuroscience$gender[final_nature_neuroscience$full_name == "Xu, Chongchong"] <- NA
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Mcrae, Jeremy"] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Vyssotski, Alexei L."] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Ölveczky, Bence P."] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Sasmita, Andrew O."] <- 1
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Szatmari-, Peter"] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "lagier-Tourenne, Clotilde"] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Wamsteeker, Jaclyn I."] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Marques, Tiago"] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "Von Schimmelmann, Melanie"] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "lagier-Tourenne, Clotilde"] <- 0
final_nature_neuroscience$bipoc[final_nature_neuroscience$full_name == "van Ede, Freek"] <- 0

final_nature_neuroscience<- final_nature_neuroscience %>% 
  distinct() 

# Read in manual labeled data in Nature Neuroscience
labeled_brain<- read.csv("cleaned_missing_value_brain.csv") %>% 
  mutate(gender = case_when(
    gender == '' ~ NA,
    TRUE ~ gender),
  bipoc = as.character(bipoc)) %>% 
  select(-first_name,-last_name)

# Merge labeled data into full name list
final_brain<- predicted_brain %>% 
  left_join(labeled_brain, by = "full_name") %>% 
  mutate(gender = coalesce(gender.x, gender.y),
         bipoc  = coalesce(bipoc.x, bipoc.y)) %>%
  select(-gender.x, -gender.y,-bipoc.x, -bipoc.y)

# Recode any NA from merging due to full name unmatching
final_brain<- final_brain %>%
  group_by(first_name, last_name) %>%
  mutate(bipoc = ifelse(is.na(bipoc), first(na.omit(bipoc)), bipoc)) %>%
  ungroup()

# Manual clean for some author name due to formatting in name (e.g. with or without initials)
final_brain$bipoc[final_brain$full_name == "Treaba, Constantina A."] <- 0
final_brain$bipoc[final_brain$full_name == "Mencacci, Niccolo E."] <- 0
final_brain$bipoc[final_brain$full_name == "Kopruszinski, Carol"] <- 0
final_brain$bipoc[final_brain$full_name == "Fonoff, Erich T."] <- 0
final_brain$bipoc[final_brain$full_name == "Korenke, G. Christoph"] <- 0
final_brain$bipoc[final_brain$last_name == "Chinnery"] <- 0
final_brain$bipoc[final_brain$last_name == "Alkuraya"] <- 0
final_brain$bipoc[final_brain$full_name == "Biessels, Geert Jan"] <- 0
final_brain$bipoc[final_brain$last_name == "Pariente"] <- 0
final_brain$bipoc[final_brain$last_name == "Caldairou"] <- 1
final_brain$bipoc[final_brain$last_name == "Bedeschi"] <- 0
final_brain$bipoc[final_brain$last_name == "Goadsby"] <- 0
final_brain$bipoc[final_brain$full_name == "Kimbrough, Dorian"] <- 1
final_brain$bipoc[final_brain$full_name == "Gaillard, William Davis"] <- 0
final_brain$bipoc[final_brain$last_name == "Havrdova"] <- 0
final_brain$bipoc[final_brain$last_name == "Laplaud"] <- 0
final_brain$bipoc[final_brain$last_name == "Aasly"] <- 0
final_brain$bipoc[final_brain$last_name == "Kamsteeg"] <- 0
final_brain$bipoc[final_brain$last_name == "Cornblath"] <- 0
final_brain$bipoc[final_brain$last_name == "Laplaud"] <- 0
final_brain$bipoc[final_brain$full_name == "Marques Jr, Wilson"] <- 0
final_brain$bipoc[final_brain$last_name == "Gelot"] <- 0
final_brain$bipoc[final_brain$last_name == "Tatsui"] <- 0
final_brain$bipoc[final_brain$last_name == "Altuzarra"] <- 0
final_brain$bipoc[final_brain$last_name == "Pariente"] <- 0
final_brain$bipoc[final_brain$last_name == "Caboclo"] <- 0
final_brain$bipoc[final_brain$last_name == "Bemelmans"] <- 0
final_brain$bipoc[final_brain$last_name == "Landwehrmeyer"] <- 0
final_brain$bipoc[final_brain$last_name == "Kyvik"] <- 0
final_brain$bipoc[final_brain$last_name == "Mehndiratta"] <- 0
final_brain$bipoc[final_brain$last_name == "Billingsley"] <- 0
final_brain$bipoc[final_brain$last_name == "Karadottir"] <- 0
final_brain$bipoc[final_brain$last_name == "Galasko"] <- 0
final_brain$bipoc[final_brain$last_name == "Baria"] <- 0
final_brain$bipoc[final_brain$last_name == "Benabid"] <- 0
final_brain$bipoc[final_brain$full_name == "Moraes Filho, Milton"] <- 0
final_brain$bipoc[final_brain$last_name == "Meinck"] <- 0
final_brain$bipoc[final_brain$full_name == "Lee, Hyo M."] <- 1
final_brain$bipoc[final_brain$last_name == "Gorson"] <- 0
final_brain$bipoc[final_brain$last_name == "Moghadam"] <- 0
final_brain$gender[final_brain$last_name == "Asmann"] <- 1
final_brain$gender[final_brain$last_name == "Benabid"] <- 0
final_brain$gender[final_brain$full_name == "Lee, Hyo M."] <- 0
final_brain$gender[final_brain$last_name == "Meinck"] <- 0
final_brain$gender[final_brain$full_name == "Liu, Jia"] <- 0
final_brain$gender[final_brain$last_name == "Jonckheere"] <- 0
final_brain$gender[final_brain$full_name == "McKenzie, Chaseley"] <- 1
final_brain$gender[final_brain$full_name == "Zhang, Wei"] <- 0
final_brain$gender[final_brain$full_name == "Hu, Michele"] <- 1
final_brain$gender[final_brain$full_name == "Hu, Michele T. M."] <- 1
final_brain$gender[final_brain$last_name == "Gerasimenko"] <- 1
final_brain$gender[final_brain$full_name == "Liu, Li"] <- 0
final_brain$gender[final_brain$first_name == "Cheney"] <- 0
final_brain$gender[final_brain$last_name == "Kuehn"] <- 1
final_brain$gender[final_brain$full_name == "Liu, Wei"] <- 0
final_brain$gender[final_brain$last_name == "Ferman"] <- 1
final_brain$gender[final_brain$last_name == "Mandelstam"] <- 1
final_brain$gender[final_brain$last_name == "Double"] <- 0
final_brain$gender[final_brain$last_name == "Lindenberger"] <- 0
final_brain$gender[final_brain$last_name == "Hsiung"] <- 0
final_brain$gender[final_brain$last_name == "Leavitt"] <- 0
final_brain$gender[final_brain$full_name == "Johnston, Blair"] <- 0

final_brain<- final_brain %>% 
  distinct() 
```

# Merge all datasets
```{r}
final<- final_jocn %>%  
  bind_rows(final_nature_neuroscience) %>% 
  bind_rows(final_brain) %>% 
  distinct(full_name, gender, bipoc)%>% 
  glimpse()
```

# Output datasets
```{r}
write.csv(final, file = "updating_name_value.csv", row.names = FALSE)
```


